### 2014-06-03 ACL2014/abstract.tex
Updated experiments, discussion

\begin{abstract}
Many applications from various domains such as web search, mobile
browsing, and NLP rely on finding the nearest neighbors of a given
text string from a large database.
Due to the very large scale of data involved 
(e.g., users' queries from commercial search engines),
computing nearest neighbors is the best way to 
%often required to
understand users' intents. 
However, it is a non-trivial
task as the computational complexity grow significantly with the number of queries.
To address this challenge, we exploit 
\lshf (a.k.a, \lsh) methods and propose 
novel varaints in a distributed computing environment (specifically, Hadoop). 
We identify several optimizations which improve performance, suitable
for deployment in very large scale settings. 
The experimental results demonstrate our 
proposed variants of \lsh achieve the robust performance with better
recall compared with ``vanilla'' \lsh,  even
when using the same space determined by the number of hash tables.

>>>>

\begin{abstract}
Many applications from various domains such as web search, mobile
browsing, and Natural Language Processing 
rely on finding the nearest neighbors of a given
text string from a large database.
Due to the very large scale of data involved 
(e.g., users' queries from commercial search engines),
computing nearest neighbors is the best way to 
%often required to
understand users' intents. 
However, it is a non-trivial
task as the computational complexity grow 
significantly with the number of queries.
To address this challenge, we exploit 
\lshf (a.k.a, \lsh) methods and propose 
novel varaints in a distributed computing environment (specifically, Hadoop). 
We identify several optimizations which improve performance, suitable
for deployment in very large scale settings. 
The experimental results demonstrate our 
proposed variants of \lsh achieve the robust performance with better
recall compared with ``vanilla'' \lsh,  even
when using the same space determined by the number of hash tables.

### 2014-06-03 ACL2014/applications.tex
Updated experiments, discussion

\section{Applications}
In this section, we highlight several examples that take significant advantage of  the approximate \dflip algorithm presented in this paper.
One of the interesting examples is to understand an intent of a user's query submitted to commercial search engines. Given a user's query,
Google, Yahoo, and Bing often delivers direct display results that summarize expected contents of the query. 
For instance, when a query ``f stock price'' is issued  to search engines, the quick summary of the stock quote with a chart is delivered 
to the user as the part of the search engine result page. By providing this direct display results, the users are expected to consume the right contents
in the first result reducing chances of unnecessary clicks. However, when query "f today closing price" is issued to search engines, the three major search engines 
fail to deliver the same direct display experience to the user query, although its query intent is strongly related to ``f stock price''. 
Therefore, by employing the \dflip, it is straightforward to build a synonym database, which helps to trigger the same direct display among related queries.
The other example is to remove duplicated instances in a result set. 
When a query set is retrieved from a repository and presented to users, it is important to remove similar queries as user experiences would be distracted from ``duplicated results.'' That is, given a set of query terms, we can apply  \dflip algorithm to build $L$ hash tables, where each hash table has $K$ width bit bucket-ids. This in turn allows to find ``duplicated query terms'' efficiently. As `duplicateness'' of among query terms typically requires ``higher'' degree of similarity than ``relatedness'', we can learn $\tau$ from training samples.  The fourth column in Table~\ref{tab:lists} illustrates several duplicate examples -- ``trumbull weather ct'' and ``weather in trumbull ct''.

>>>>

\section{Applications}
In this section, we highlight several examples that take significant advantage of  the approximate \dflipb algorithm presented in this paper.
One of the interesting examples is to understand an intent of a user's query submitted to commercial search engines. Given a user's query,
Bing, Google, and Yahoo often delivers direct display results that summarize expected contents of the query. 
For instance, when a query ``f stock price'' is issued  to search engines, the quick summary of the stock quote with a chart is delivered 
to the user as the part of the search engine result page. By providing this direct display results, the users are expected to consume the right contents
in the first result reducing chances of unnecessary clicks. However, when query "f today closing price" is issued to search engines, the three major search engines 
fail to deliver the same direct display experience to the user query, although its query intent is strongly related to ``f stock price''. 
Therefore, by employing the \dflip, it is straightforward to build a synonym database, which helps to trigger the same direct display among related queries.
The other example is to remove duplicated instances in a result set. 
When a query set is retrieved from a repository and presented to users, it is important to remove similar queries as user experiences would be distracted from ``duplicated results.'' 
That is, given a set of query terms, we can apply  \dflipb algorithm to build a lookup table of near-duplicates 
to find ``duplicated query terms'' efficiently. As ``duplicateness'' of among query terms typically requires ``higher'' degree of similarity (relatively easier problem) than ``relatedness'', we can tune parameters ($K, L, F$) based on a specific $\tau$ (e.g $\tau=0.9$) from training samples.  The fourth column in Table~\ref{tab:lists} illustrates several duplicate examples -- ``trumbull weather ct'' and ``weather in trumbull ct''.

### 2014-06-03 ACL2014/discussion.tex
Updated experiments, discussion

\section{Discussion and Conclusion}
\label{sec:discuss}
%In this paper, we demonstrated the effectiveness of our p

>>>>

\section{Discussion and Conclusion}
\label{sec:discuss}
In this section, we highlight several examples that take significant advantage of  the approximate \dflipb algorithm presented in this paper.
One of the interesting examples is to understand an intent of a user's query submitted to commercial search engines. Given a user's query,
Bing, Google, and Yahoo often delivers direct display results that summarize expected contents of the query. 
For instance, when a query ``f stock price'' is issued  to search engines, the quick summary of the stock quote with a chart is delivered 
to the user as the part of the search engine result page. By providing this direct display results, the users are expected to consume the right contents
in the first result reducing chances of unnecessary clicks. However, when query "f today closing price" is issued to search engines, the three major search engines 
fail to deliver the same direct display experience to the user query, although its query intent is strongly related to ``f stock price''. 
Therefore, by employing the \dflipb, it is straightforward to build a synonym database, which helps to trigger the same direct display among related queries.

The other example is to remove duplicated instances in a result set. 
When a query set is retrieved from a repository and presented to users, it is important to remove similar queries as user experiences would be distracted from ``duplicated results.'' 
That is, given a set of query terms, we can apply  \dflipb algorithm to build a lookup table of near-duplicates 
to find ``duplicated query terms'' efficiently. As ``duplicateness'' of among query terms typically requires ``higher'' degree of similarity (relatively easier problem) than ``relatedness'', we can tune parameters ($K, L, F$) based on a specific $\tau$ (e.g $\tau=0.9$) from training samples.  The fourth column in Table~\ref{tab:lists} illustrates several duplicate examples -- ``trumbull weather ct'' and ``weather in trumbull ct''.

### 2014-06-03 ACL2014/experiments.tex
Updated experiments, discussion

\begin{table}
\centering
\begin{tabular}{|c|rc|rc|}
\hline
\multirow{2}{*}{$\tau$}  & \multicolumn{2}{c}{\small \aol} & \multicolumn{2}{c}{\small \dataA} \\
 & {\small Comparisons} & {\small Recall} & {\small Comparisons} & {\small Recall}  \\
\hline
0.7 & \multirow{3}{*} {57}  & .63  & \multirow{3}{*} {1052} & .67 \\
0.8 &   & .84  &  & .81 \\
0.9 &   & .98  &  & .96 \\
\hline 
 \end{tabular}
\caption{\footnotesize{Varying $\tau$ with fixed $K=16$ and $L=10$ on \aol and \dataA.}}
\label{tab:varyTau}
\end{table}

@@

In the second experiment, we vary $L$ to be in $\{1,10,28,55\}$ while fixing $K=16$ on the \aol and \dataA datasets. 
Recal that $L$ denotes the number of hash tables and $K$ the length of the index of the buckets in the table. 
Increasing $K$ results in increase of the precision by reducing the false positive candidates, but 
the $L$ also need to be correspondingly increased in order the maintain a good recall
(i.e. reduce false negatives). 
Table \ref{tab:varyL} shows that increasing $L$ leads to better recall, 
but at the expense of performing more comparisons on both the datasets. 
In addition, having a large $L$ 
means generating large number of random projection bits and hash tables which is 
both time and memory intensive. Hence, we fix $L=10$, 
which leads to a reasonable recall with a tolerable number of comparisons.

\begin{table}
\centering
\begin{tabular}{|c|rc|rc|}
\hline
\multirow{2}{*}{L} & \multicolumn{2}{c}{\small \aol} & \multicolumn{2}{c}{\small \dataA} \\
 & {\small Comparisons} & {\small Recall} & {\small Comparisons} & {\small Recall}  \\
\hline
1 & 7  & .28 & 106 & .36 \\
 \rowcolor[gray]{0.9} 10  &  57 & .63 & 1052 & .67 \\
28 &  152 & .77 & 2908 & .78 \\
55 &  297 & .89 & 5648 & .84 \\
\hline 
 \end{tabular}
\caption{\footnotesize{Varying $L$ with fixed $K=16$ on \aol and \dataA with $\tau=0.7$.}}
\label{tab:varyL}
\end{table}
In the third experiment, we vary $K$ to be in $\{4,8,16\}$ while fixing $L=10$ on \aol and \dataA datasets. 
As expected, Table \ref{tab:varyK} shows that increasing $K$ reduces the number of 
comparisons and worsens recall on both the datasets. This is intuitive as  
the larger value of $K$ leads to larger 
gap between probabilites of collision between close queries 
and far queries (see Section \ref{sec:vlsh}). 
Hence, we fix $K=16$ to have few number of comparisons.

\begin{table}
\centering
%\begin{tabular}{|c|r|c|}
\begin{tabular}{|c|rc|rc|}
\hline
%$K$ & Comparisons & Recall \\
\multirow{2}{*}{K} & \multicolumn{2}{c}{\small \aol} & \multicolumn{2}{c}{\small \dataA} \\
 &{\small Comparisons} & {\small Recall} & {\small Comparisons} & {\small Recall}   \\
\hline
4  &  112,347 & .98 & 2,29,2670 & .96 \\
8 &  11,008 & .90 & 221,132 & .88 \\
\rowcolor[gray]{0.9}16 &  57 & .63 & 1,052 & .67 \\
\hline 
 \end{tabular}
\caption{\footnotesize{Varying $K$ with fixed $L=10$ on \aol with $\tau=0.7$.}}
\label{tab:varyK}
\end{table}

@@

\subsection{Evaluating Multi-Probe LSH}
\label{subsec:eval:multiProbeLSH}
In the first experiment, we compare flipping the bits in query only. 
We evaluate two approaches: \rflipq and \dflipq. We can make several observations from Table \ref{tab:query:aol}: 1) As expected, increasing the number of flips improve recall at expense of more comparisons for both \dflipq and \rflipq. 2) Our results show that \dflipq has significantly better recall than \rflipq with similar number of comparisons.
In second row of the table with $F=2$, \dflipq has nine points better recall than \rflipq.

In the second experiment, we compare flipping the bits in both query and the dataset. 
We can make similar observations from Table \ref{tab:both:aol} as made in the first experiment. 
In the second row of the Table with $F=2$, \dflipb has thirteen points better recall than \rflipb with similar number of comparisons. 
Comparing across second row of  Table \ref{tab:query:aol} and \ref{tab:both:aol} shows that flipping the bits in both query and the dataset has better 
recall at the expense of more comparisons. This is expected as flipping both means that we can find queries at distance two (one flip in query, one flip in dataset), 
hence more queries in each table when we do probe. Note, we also compared distance based flipping with random flipping on different sized data-sets, 
and found distance based flipping is always significantly better in terms of recall as compared to random flipping.

In the third experiment, we show the results of both variants of distance based Multi Probe that is \dflipq and \dflipb on different sized datasets. 
Table \ref{tab:dataset:final} shows the results with parameter $L=10$, $F=2$, and data-size dependent $K$ (same settings of $K$ for different sized datasets
is used as in the last experiment of Section \ref{subsec:eval:vanillaLSH}). As observed in the last experiment, flipping bits in both query and the dataset
is significantly better in terms of recall (eight points on \dataA and \dataB) with more number of comparisons.

In the fourth experiment, Table \ref{tab:lists} shows the qualitative results for some arbitrary queries. These results are found by applying our
system (\dflipb with parameters $L=10$, $K=24$, and $F=2$ ) on \dataC. The first two columns in Table \ref{tab:lists} show that the returned approximate 
similar neighbors can be useful in finding related queries \cite{Jones06WWW,Jain11SIGIR}. The third column shows an example, where we can find several popular spell errors. 
The last column shows different variants of a query, where user intends to find out the ``weather in trumbull ct''. 
Modern search engines provide a direct display with respect to ``weather'' related queries. 
Hence, if we don't have enough evidence about a specific query being related to ``weather'', we can use queries approximately similar to it to infer that 
if this query is about ``weather'' or not.

\begin{table}
\centering
{
\small \addtolength{\tabcolsep}{-4.5pt}
\begin{tabular}{|c|cc|cc|} 
\hline
Method & \multicolumn{2}{c}{\rflipq} & \multicolumn{2}{c}{\dflipq}   \\
\hline
$F$ & Comparisons & Recall  & Comparisons & Recall \\
\hline
1 & 108 & .65 & 106 & .72 \\
2 & 159 & .66 &  {\it155} & {\bf .75}  \\
5 &  311 & .70 &  {\it 303} & {\bf .79}  \\
\hline 
 \end{tabular}
 }
\caption{\footnotesize{Flipping the bits in the query only with $K=16$ and $L=10$ on \aol  with $\tau=0.7$.}}
\label{tab:query:aol}
\end{table}

\begin{table}
\centering
{
\small \addtolength{\tabcolsep}{-4.5pt}
\begin{tabular}{|c|cc|cc|} 
\hline
Method & \multicolumn{2}{c}{\rflipb} & \multicolumn{2}{c}{\dflipb}   \\
\hline
$F$ & Comparisons & Recall  & Comparisons & Recall \\
\hline
1 & 204 & .71 & 192 & .80 \\
 2 & 433 & .73    &  {\it 405} & {\bf .86}  \\
5 &  1557 & .86  & 1475 & .93     \\
\hline 
 \end{tabular}
 }
\caption{\footnotesize{Flipping the bits in both the query and the dataset with $K=16$ and $L=10$ on \aol  with $\tau=0.7$.}}
\label{tab:both:aol}
\end{table}

\begin{table}
\centering
{
\small \addtolength{\tabcolsep}{-4.5pt}
\begin{tabular}{|c|cc|cc|} 
\hline
Method & \multicolumn{2}{c}{\dflipq} & \multicolumn{2}{c}{\dflipb}   \\
\hline
{\small Data} & {\small Comps.} & {\small Recall}  & {\small Comps.} & {\small Recall} \\
\hline
{\small \aol ($K=16$)} & 155 & .75 & 405 & .86 \\
{\small \dataA ($K=16$)} & 2980 & .76  & 7904  & .84   \\
{\small \dataB ($K=20$)} & 1954  & .64 & 5242  & .72     \\
{\small \dataC ($K=24$)} & 1280  & -  & 3427 & -      \\
\hline 
 \end{tabular}
 }
\caption{\footnotesize{Best parameter settings (Based on minimizing number of comparisons and maximizing recall) of $K$ with fixed $L=10$ and $F=2$ on different sized datasets with $\tau=0.7$.}}
\label{tab:dataset:final}
\end{table}

@@

>>>>

\begin{table}
\centering
\begin{tabular}{|c|rc|rc|}
\hline
\multirow{2}{*}{$\tau$}  & \multicolumn{2}{c|}{\small \aol} & \multicolumn{2}{c|}{\small \dataA} \\
 & {\small Comparisons} & {\small Recall} & {\small Comparisons} & {\small Recall}  \\
\hline
0.7 & \multirow{3}{*} {57}  & .63  & \multirow{3}{*} {1052} & .67 \\
0.8 &   & .84  &  & .81 \\
0.9 &   & .98  &  & .96 \\
\hline 
 \end{tabular}
\caption{\footnotesize{Varying $\tau$ with fixed $K=16$ and $L=10$ on \aol and \dataA.}}
\label{tab:varyTau}
\end{table}

@@

In the second experiment, we vary $L$ to be in $\{1,10,28,55\}$ while fixing $K=16$ on the \aol and \dataA datasets. 
Recal that $L$ denotes the number of hash tables and $K$ is the width of the index of the buckets in the table. 
Increasing $K$ results in increase of the precision by reducing the false positive candidates, but 
the $L$ also need to be correspondingly increased in order the maintain a good recall
(i.e. reduce false negatives). 
Table \ref{tab:varyL} shows that increasing $L$ leads to better recall, 
but at the expense of performing more comparisons on both the datasets. 
In addition, having a large $L$ 
means generating large number of random projection bits and hash tables which is 
both time and memory intensive. Hence, we fix $L=10$, 
which leads to a reasonable recall with a tolerable number of comparisons.

\begin{table}
\centering
\begin{tabular}{|c|rc|rc|}
\hline
\multirow{2}{*}{L} & \multicolumn{2}{c|}{\small \aol} & \multicolumn{2}{c|}{\small \dataA} \\
 & {\small Comparisons} & {\small Recall} & {\small Comparisons} & {\small Recall}  \\
\hline
1 & 7  & .28 & 106 & .36 \\
 \rowcolor[gray]{0.9} 10  &  57 & .63 & 1052 & .67 \\
28 &  152 & .77 & 2908 & .78 \\
55 &  297 & .89 & 5648 & .84 \\
\hline 
 \end{tabular}
\caption{\footnotesize{Varying $L$ with fixed $K=16$ on \aol and \dataA with $\tau=0.7$.}}
\label{tab:varyL}
\end{table}
In the third experiment, we vary $K$ to be in $\{4,8,16\}$ while fixing $L=10$ on \aol and \dataA datasets. 
As expected, Table \ref{tab:varyK} shows that increasing $K$ reduces the number of 
comparisons and worsens recall on both the datasets. This is intuitive as  
the larger value of $K$ leads to larger 
gap between probabilites of collision between close queries 
and far queries (see Section \ref{sec:vlsh}). 
Hence, we fix $K=16$ to have few number of comparisons.

\begin{table}
\centering
%\begin{tabular}{|c|r|c|}
\begin{tabular}{|c|rc|rc|}
\hline
%$K$ & Comparisons & Recall \\
\multirow{2}{*}{K} & \multicolumn{2}{c|}{\small \aol} & \multicolumn{2}{c|}{\small \dataA} \\
 &{\small Comparisons} & {\small Recall} & {\small Comparisons} & {\small Recall}   \\
\hline
4  &  112,347 & .98 & 2,29,2670 & .96 \\
8 &  11,008 & .90 & 221,132 & .88 \\
\rowcolor[gray]{0.9}16 &  57 & .63 & 1,052 & .67 \\
\hline 
 \end{tabular}
\caption{\footnotesize{Varying $K$ with fixed $L=10$ on \aol with $\tau=0.7$.}}
\label{tab:varyK}
\end{table}

@@

\begin{table}
\centering
{
\small \addtolength{\tabcolsep}{-4.5pt}
\begin{tabular}{|c|cc|cc|} 
\hline
Method & \multicolumn{2}{c|}{\rflipq} & \multicolumn{2}{c|}{\dflipq}   \\
\hline
$F$ & Comparisons & Recall  & Comparisons & Recall \\
\hline
1 & 108 & .65 & 106 & .72 \\
2 & 159 & .66 &  {\it155} & {\bf .75}  \\
5 &  311 & .70 &  303 &  .79  \\
10 & 557  & .75 &  552 &  .81  \\
16 & 839   & .82 &  839 &  .82  \\
\hline 
 \end{tabular}
 }
\caption{\footnotesize{Flipping the bits in the query only with $K=16$ and $L=10$ on \aol  with $\tau=0.7$.}}
\label{tab:query:aol}
\end{table}

\begin{table}
\centering
{
\small \addtolength{\tabcolsep}{-4.5pt}
\begin{tabular}{|c|cc|cc|} 
\hline
Method & \multicolumn{2}{c|}{\rflipb} & \multicolumn{2}{c|}{\dflipb}   \\
\hline
$F$ & Comparisons & Recall  & Comparisons & Recall \\
\hline
1 & 204 & .71 & 192 & .80 \\
 2 & 433 & .73    &  {\it 405} & {\bf .86}  \\
5 &  1557 & .86  & 1475 & .93     \\
10 &  4138 & .94 & 4059 & .96     \\
16 &  5922 & .96 & 5922 & .96     \\
\hline 
 \end{tabular}
 }
\caption{\footnotesize{Flipping the bits in both the query and the database with $K=16$ and $L=10$ on \aol  with $\tau=0.7$.}}
\label{tab:both:aol}
\end{table}

\begin{table}
\centering
{
\small \addtolength{\tabcolsep}{-4.5pt}
\begin{tabular}{|c|cc|cc|} 
\hline
Method & \multicolumn{2}{c|}{\dflipq} & \multicolumn{2}{c|}{\dflipb}   \\
\hline
{\small Data} & {\small Comps.} & {\small Recall}  & {\small Comps.} & {\small Recall} \\
\hline
{\small \aol ($K=16$)} & 155 & .75 & 405 & .86 \\
{\small \dataA ($K=16$)} & 2980 & .76  & 7904  & .84   \\
{\small \dataB ($K=20$)} & 1954  & .64 & 5242  & .72     \\
{\small \dataC ($K=24$)} & 1280  & -  & 3427 & -      \\
\hline 
 \end{tabular}
 }
\caption{\footnotesize{Best parameter settings (Based on minimizing number of comparisons and maximizing recall) of $K$ with fixed $L=10$ and $F=2$ on different sized datasets with $\tau=0.7$.}}
\label{tab:dataset:final}
\end{table}

@@

\subsection{Evaluating Multi-Probe LSH}
\label{subsec:eval:multiProbeLSH}
In the first experiment, we compare flipping the bits in query only. 
We evaluate two approaches: \rflipq and \dflipq. We can make several observations from Table \ref{tab:query:aol}: 1) As expected, increasing the number of flips improve recall at expense of more comparisons for both \dflipq and \rflipq. 2) The last row of the Table \ref{tab:query:aol} shows that once we flip all the $K$ bits ($F=16$),  \dflipq and \rflipq converge to the same algorithm.  3) Our results show that \dflipq has significantly better recall than \rflipq with similar number of comparisons. In second row of the table with $F=2$, \dflipq has nine points better recall than \rflipq.

In the second experiment, we compare flipping the bits in both query and the database. 
We can make similar observations from Table \ref{tab:both:aol} as made in the first experiment. 
In the second row of the Table with $F=2$, \dflipb has thirteen points better recall than \rflipb with similar number of comparisons. 
Comparing across second row of  Table \ref{tab:query:aol} and \ref{tab:both:aol} shows that flipping the bits in both query and the database has better 
recall at the expense of more comparisons. This is expected as flipping both means that we can find queries at distance two (one flip in query, one flip in database), 
hence more queries in each table when we probe. Note, we also compared distance based flipping with random flipping on different sized data-sets, 
and found that distance based flipping is always significantly better in terms of recall as compared to random flipping.\footnote{Due to limited space, we omit those results.}

We select $F=2$ as the best parameter setting with goal of maximizing recall by restricting comparisons to minimum. For better recall at expense of more comparisons, $F=5$ can also be selected. However, results in Table \ref{tab:query:aol} and \ref{tab:both:aol} indicate that $F>5$ does \emph{not} increase recall significantly and at the same time leads to more number of comparisons.

In the third experiment, we show the results of both variants of distance based Multi Probe that is \dflipq and \dflipb on different sized datasets. 
Table \ref{tab:dataset:final} shows the results with parameter $L=10$, $F=2$, and data-size dependent $K$ (same settings of $K$ for different sized datasets
as used in the last experiment of Section \ref{subsec:eval:vanillaLSH}).  As observed in the last experiment, flipping bits in both query and the database
is significantly better in terms of recall with more number of comparisons. The second and third row of the table respectively 
shows that flipping bits in both query and the database has eight points better recall on both \dataA and \dataB 
datasets. With the goal of maximizing recall with some extra comparisons, we select \dflipb as our final algorithm. 
\dflipb maximizes recall with small number of tables and comparisons. 
On our entire corpus (\dataC) with hundreds of millions of queries, 
\dflipb only requires $3,427$ comparisons compared to hundreds of millions of comparisons by exact brute force algorithm.  
\dflipb returns $9$ neighbors on average per given query; averaged over $2000$ random test 
queries.\footnote{As many queries can be long, hence such queries only have few neighbors.}

In the fourth experiment, Table \ref{tab:lists} shows the qualitative results for some arbitrary queries. These results are found by applying our
system (\dflipb with parameters $L=10$, $K=24$, and $F=2$ ) on \dataC. The second column in Table \ref{tab:lists} shows that the returned approximate 
similar neighbors can be useful in finding related queries \cite{Jones06WWW,Jain11SIGIR}. 
The third column shows an example, where we can find several popular spellling errors. 
The first and last column show examples of near-duplicate queries \cite{leeCIKM11}.

%different variants of a query, where user intends to find out the ``weather in trumbull ct''. 
%Modern search engines provide a direct display with respect to ``weather'' related queries. 
%Hence, if we don't have enough evidence about a specific query being related to ``weather'', we can use queries approximately similar to it to infer that 
%if this query is about ``weather'' or not.

### 2014-06-03 ACL2014/intro.tex
Updated experiments, discussion

 \section{Introduction}
Every day, 
hundreds of millions of users visit commercial search engines to pose
queries on topics of their interest.  
Such queries are typically just a few key words intended to specify
the topic that the user has in mind. 
To provide users with a high quality service, 
search engines such as Bing, Google, and Yahoo require
intelligent analysis to realize users' implicit intents.
The key resource that they have to help tease out what is meant is
their large history of requests, in the form of large scale query logs.  
A key primitive in 
%One of the key interesting tasks involved in 
learning users' implicit intents is the computation of 
nearest neighbors (queries) for a user given query. 
Computing nearest neighbors is useful for 
many search-related problems on the Web and the Mobile such as 
finding related queries \cite{Jones06WWW,Jain11SIGIR,Song12WSDM}, 
finding near-duplicate queries \cite{}, spelling correction \cite{},  
paraphrasing \cite{petrovicNAACL12,ganitkevitch13Paraphrase}, 
and diversifying search results \cite{Song11SIGIR}.

@@

Our work makes the following contributions: 
\begin{enumerate}
\item We begin with a ``vanilla'' \lsh algorithm based on the seminal
  research of Andoni and Indyk  \shortcite{Andoni08CACM}.
 To best of our knowledge, this is the first paper that applies this algorithm to NLP applications. 
\item We propose four novel variants of vanilla LSH motivated by the
  research on Multi-Probe LSH \cite{LvVLDB07}.  We show that two of
  our variants achieve significantly better recall than the vanilla
  \lsh by using the same number of hash tables. The main idea behind
  these variants is to intelligently probe multiple ``nearby'' buckets within a table that have a high probability of containing the nearest neighbors of a query.  
\item We present a framework on Hadoop that efficiently finds nearest neighbors for a given query from a commercial large-scale query logs in sublinear time. % Can we claim something more specific wrt time (e.g. 0(N logN))?
%: Random Flipping and Query-Driven Flipping. 
\item  We show that the applicability of our system on two real-world
  applications: finding related queries and removing (near) duplicate
  queries.
The system outperforms competitor methods, and is currently being
implemented for production use within a large search provider. 
%(Increasing  direct display coverage is related to finding related queries) and ??.
\end{enumerate}

%We are interested in the following setting: given a large set of 
%points $q_1,q_2,\dots,q_n$, each of them is a search-query.

%Spelling {grouping mis-spellings in same group}
%Similar entities {LOTR,}
%Finding related queries

>>>>

 \section{Introduction}
Every day, 
hundreds of millions of users visit commercial search engines to pose
queries on topics of their interest.  
Such queries are typically just a few key words intended to specify
the topic that the user has in mind. 
To provide users with a high quality service, 
search engines such as Bing, Google, and Yahoo require
intelligent analysis to realize users' implicit intents.
The key resource that they have to help tease out what is meant is
their large history of requests, in the form of large scale query logs.  
A key primitive in 
%One of the key interesting tasks involved in 
learning users' implicit intents is the computation of 
nearest neighbors (queries) for a user given query. 
Computing nearest neighbors is useful for 
many search-related problems on the Web and the Mobile such as 
finding related queries \cite{Jones06WWW,Jain11SIGIR,Song12WSDM}, 
finding near-duplicate queries \cite{leeCIKM11}, spelling correction \cite{ahmadEMNLP05,liSIGIR12},  
and diversifying search results \cite{Song11SIGIR}; and many Natural Language Processing (NLP) tasks   
such as paraphrasing \cite{petrovicNAACL12,ganitkevitch13Paraphrase}, 
distributional similarity \cite{ravichandran05,agirre09,turneyVector10}, and creating sentiment lexicons from large-scale Web data \cite{velikovich10}.

@@

Our work makes the following contributions: 
\begin{enumerate}
\item We begin with a ``vanilla'' \lsh algorithm based on the seminal
  research of Andoni and Indyk  \shortcite{Andoni08CACM}.
 To best of our knowledge, this is the first paper that applies this algorithm to NLP applications. 
\item We propose four novel variants of vanilla LSH motivated by the
  research on Multi-Probe LSH \cite{LvVLDB07}.  We show that two of
  our variants achieve significantly better recall than the vanilla
  \lsh by using the same number of hash tables. The main idea behind
  these variants is to intelligently probe multiple ``nearby'' buckets within a table that have a high probability of containing the nearest neighbors of a query.  
\item We present a framework on Hadoop that efficiently finds nearest neighbors for a given query from a commercial large-scale query logs in sublinear time. % Can we claim something more specific wrt time (e.g. 0(N logN))?
%: Random Flipping and Query-Driven Flipping. 
\item  We discuss the applicability of our framework on two real-world
  applications: finding related queries and removing (near) duplicate
  queries. The algorithms presented in this paper are currently being
implemented for production use within a large search provider. 
%(Increasing  direct display coverage is related to finding related queries) and ??.
\end{enumerate}

%We are interested in the following setting: given a large set of 
%points $q_1,q_2,\dots,q_n$, each of them is a search-query. 
%Spelling {grouping mis-spellings in same group}
%Similar entities {LOTR,}
%Finding related queries
